Reproducible Summary Tables with the gtsummary Package

### 2020-12-11 RJtemplate_gtsummary_submission.tex

# summarize data
svy_api %>%
  tbl_svysummary(by = cname, 
                 include = c(growth, target, cname),
                 label = list(growth ~ "Growth",
                              target ~ "Target")) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{svysummary.png}
  \centering
\end{figure}

@@

@@

>>>>

# summarize data
svy_api %>%
  tbl_svysummary(by = cname, 
                 include = c(growth, target, cname),
                 label = list(growth ~ "Growth",
                              target ~ "Target")) %>%
  add_p()
\end{example}
\begin{figure}[H]
  \includegraphics[height=4cm]{svysummary.png}
  \centering
\end{figure}

@@

The gtsummary package utilizes the gt package\citep{gt} to print the summary tables.
The gt package exports approximately one hundred functions to customize and style tables.
When you need to add additional details or styling not available within gtsummary, use the \texttt{as\_gt()} to convert the gtsummary object to gt and continue customization.

\begin{example}

\end{example}

@@

SHOULD WE JUST REMOVE THIS SECTION?!

\begin{figure}[h!]
  \includegraphics[height=4.5cm]{print_engines.png}
  \centering
\end{figure}

\section{Summary}
